\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-16 paper/paper 2/dc-2015.tex
minor

\section{Motivation}
\label{sec:motivation}
Even with an upcoming W3C recommendation, it can be expected that several constraint languages will be used in practice in future -- consider the situation in the XML world, where a standardized schema language was available from the beginning and yet additional ways to formulate and check constraints have been created. Therefore, 
semantically equivalent \emph{specific constraints} represented in different languages will exist.
This raises two questions: 
\begin{enumerate}
 \item How can we ensure that two semantically equivalent constraints are actually validated consistently?
 \item How can we support the transformation of semantically equivalent constraints from one contraint language to another?
\end{enumerate}

\paragraph{Consistent implementation.}
Even though SPIN provides a convenient way to represent constraints and to validate data according to these constraints, the implementation of a high-level constraint language still requires a tedious mapping to SPIN with a certain degree of freedom as to how a constraint violation is actually represented and how exactly the violation of the contraint is checked.
Our framework therefore proides a common ground that is solely based on the abstract definitions of the constraint types, as identified in our database. By providing a \emph{SPIN} mapping
for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}}, it is ensured that the details of the SPIN implementation are consistent irrespective of the constraint language and that the validation leads always to exactly the same results.

@@

The properties describing a simple constrained are very structural. The central property is the \emph{constraining element} which refers to one of 103 contraining elements described in our technical report \cite{BoschNolleAcarEckert2015}. Constraining elements are for example taken from Description Logics, another concrete example would be 'REGEX' where a regular expression is checked against some property value. In most cases, constraining elements directly correspond to a constraint type, sometimes (as for REGEX) they are shared by several constraint types. Complex constraints again need several constraing elements to be expressed.

Irrespective of and additonal to the constraining element, there are properties to describe the actual constraint, they can also be seen as parameters for the constraining element. The \emph{context class} limits the constraint to individuals of a specific class. Depending on the constraining elements, a list of \emph{classes} can be provided, for example to determine the valid classes for a value or to define a class intersection to be used in a constraint. \emph{leftProperties} and \emph{rightProperties} are lists usually containing properties the constraint is applied to. A typical example for a constraint with a right hand side list of properties would be R43, literal value comparision, where constraints like birthDate $<$ deathDate can be expressed.

Finally, the \emph{constrainig value} contains a literal value to be checked against; for instance in the case of the 'REGEX' element, it contains the regular expression to be evaluated.

>>>>

\section{Motivation}
\label{sec:motivation}
Even with an upcoming W3C recommendation, it can be expected that several constraint languages will be used in practice in future -- consider the situation in the XML world, where a standardized schema language was available from the beginning and yet additional ways to formulate and check constraints have been created. Therefore, 
semantically equivalent \emph{specific constraints} represented in different languages will exist.
This raises two questions: 
\begin{enumerate}
 \item How can we ensure that two semantically equivalent constraints are actually validated consistently?
 \item How can we support the transformation of semantically equivalent constraints from one constraint language to another?
\end{enumerate}

\paragraph{Consistent implementation.}
Even though SPIN provides a convenient way to represent constraints and to validate data according to these constraints, the implementation of a high-level constraint language still requires a tedious mapping to SPIN with a certain degree of freedom as to how a constraint violation is actually represented and how exactly the violation of the constraint is checked.
Our framework therefore provides a common ground that is solely based on the abstract definitions of the constraint types, as identified in our database. By providing a SPIN mapping
for each constraint type\footnote{RDF-CV to SPIN online available at: \url{https://github.com/boschthomas/RDF-CV-2-SPIN}\label{RDF-CV-2-SPIN}}, it is ensured that the details of the SPIN implementation are consistent irrespective of the constraint language and that the validation leads always to exactly the same results.

@@

The properties describing a simple constrained are very structural. The central property is the \emph{constraining element} which refers to one of 103 constraining elements described in our technical report \cite{BoschNolleAcarEckert2015}. Constraining elements are for example taken from Description Logics, another concrete example would be 'REGEX' where a regular expression is checked against some property value. In most cases, constraining elements directly correspond to a constraint type, sometimes (as for REGEX) they are shared by several constraint types. Complex constraints again need several constraining elements to be expressed.

Irrespective of and additional to the constraining element, there are properties to describe the actual constraint, they can also be seen as parameters for the constraining element. The \emph{context class} limits the constraint to individuals of a specific class. Depending on the constraining elements, a list of \emph{classes} can be provided, for example to determine the valid classes for a value or to define a class intersection to be used in a constraint. \emph{leftProperties} and \emph{rightProperties} are lists usually containing properties the constraint is applied to. A typical example for a constraint with a right hand side list of properties would be R43, literal value comparison, where constraints like birthDate $<$ deathDate can be expressed.

Finally, the \emph{constraining value} contains a literal value to be checked against; for instance in the case of the 'REGEX' element, it contains the regular expression to be evaluated.
